Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-18 paper/main.tex
rearrange blocks of text in discussion

\begin{itemize}
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
    wurde
    \item location of tables \& figures is pretty confusing at the moment
\end{itemize}

@@

\todo[inline]{for completeness, contrasts are mentioned in the method section.
Shall results be reported (and later discussed)?}

@@

\subsection{group level: AD \& AV (PPA only)}

@@

@@

% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AD and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This larger extension, especially into the primary visual cortex, can be
attributed to the fact that we averaged the content of individual frames after a
cut and did not control for confounding features like depicted faces or
objects,and low-level visual features.
% cross-modal control purpose?
\todo[inline]{better frame that it is conceptual/cross-modal control; but what
do the results tell us? yes, it ``kinda works'' but \dots?}
\todo[inline]{concluding statement regarding AV vs AD and cross-modality of
results?}

\subsection{robustness of contrasts}

% why we did a couple of contrasts
For both stimuli we created several contrasts that varied the amount of events
available for the analysis and how well the annotated events within categories
on average matched the stimulus type that we assumed to be preferentially
processed in the PPA.
% PPA AD
Regarding contrasts of the AD stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA overlap.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but also extending into more posterior brain
regions.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust across contrasts do not depend on the design of one specific
contrasts.

@@

\subsection{consistencies across contrasts}

@@

\subsection{individual analyses}

>>>>

\begin{itemize}
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
    wurde
    \item location of tables \& figures is pretty confusing at the moment
    \item length of report of other reliably significant cluster across
        contrasts and report of control contrasts depends on if/how long they
        should be discussed
\end{itemize}

@@

\todo[inline]{contrasts are mentioned in the method section; shall results be
reported (and later discussed)?}

@@

\subsection{PPA; AV \& AD; group \& individuals}

\subsubsection{AV: group}
% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AD and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This larger extension, especially into the primary visual cortex, can be
attributed to the fact that we averaged the content of individual frames after a
cut and did not control for confounding features like depicted faces or
objects,and low-level visual features.
% cross-modal control purpose?
\todo[inline]{better frame that it is conceptual/cross-modal control; but what
do the results tell us? yes, it ``kinda works'' but \dots?}
\todo[inline]{concluding statement regarding AV vs AD and cross-modality of
results?}

@@

\subsubsection{AD: group}

@@

\todo[inline]{individual results should be incorporated into above section;
depends on long discussion of individual results will be}

\subsubsection{AD: individuals}

\subsection{Robust (results) across contrasts}

% why we did a couple of contrasts
For both stimuli we created several contrasts that varied the amount of events
available for the analysis and how well the annotated events within categories
on average matched the stimulus type that we assumed to be preferentially
processed in the PPA.

\subsubsection{PPA}
% PPA AD
Regarding contrasts of the AD stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA overlap.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but also extending into more posterior brain
regions.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust across contrasts do not depend on the design of one specific
contrasts.

@@

@@
